\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Requirements Analysis Report}
\author{Nikaela Balla
\and Mishkat Haider Chowdhury
\and Mauricio Guillermo Loza Arze}

\date{March 2023}

\begin{document}

\maketitle

\section{ Problem to be solved}
\label{sec:problem}
The purpose of this project is to make a SmartTable.Why would we need this? 
Well, imagine you are in a crowded restaurant. You have to wait for the host to bring you to a table that isn't reserved. Once you sit down,
you will need to grab the waiters attention to order and then to get the bill. This is a lot of work for people with social anxiety or people 
who are disabled. That is the problem our table is implemented to fix. 
\section{ Introduction}
Our intended users are: a client in a restaurant and the waiter in said restaurant or other service based establishments.
The client has difficulties communicating with others, because of social anxiety, disability or other reasons. The waiter is overworked and
needs the help of the SmartTable to lessen his workload.
The different options for our interface implementation: \begin{itemize}
    \item Gesture based interface using a leap motion sensor \cite{zaicti2015free}.
    \item  Voice control commands using a phone application.
    \item  Gestures based interface using conventional cameras (opencv).
    \item A remote with buttons for changing the colors.
\end{itemize}

\subsection{Experience Sequence }
The customer enters the restaurant.The table has Led lights on it's side that indicate the different states it has.
\begin{itemize}
    \item Table is green by default.
    \item  When the client sits on the table, it's color changes to red.It uses simple pressure sensors to tell when someone is sitting \cite{cheng2013smart}.
    \item When the client wants to request the waiter's attention, they make a gesture, speak to the app or press a button. 
    Table changes color from  red to blue.
    \item  There is  a timer which turns darker blue the more the client waits.
    \item Waiter approaches and turns off timer in a similar way to client, resets table status and it goes back to the color red.
    \item When the client requests the bill with a gesture, voice or button, table changes color to yellow.
    \item When the client sets the table to "do not disturb" in the same way as above, table changes color to white.
    \item Waiter sets table to reserved status similarly as above, the table than changes to red.
\end{itemize}
This proccess will be explained in more detail in the requirements section.
\section{Requirements}
\subsection{Functional requirements}
\begin{itemize}
    \item The system should identify when a user is sited on the table.
    \item The system should provide a hand gesture interface for the user (client, waiter) to input commands.
    \item The system should show visually the confirmation of a command executed by the user (client, waiter).
    \item The system should show visually the current state of the table.
\end{itemize}
\subsection{Data requirements}
\subsection{Environmental requirements}
\begin{itemize}
    \item The system visual indicators should be visible in low lighting conditions.
    \item The system visual indicators should be visible in high lighting conditions.
    \item The system interface should be able to work under low light conditions.
    \item The system interface should be able to work under high lighting conditions.
    \item The system visual indicators should be visible from a 360.
    \item The system should be accompanied by a pamphlet that should show in a simple and understandable way how to execute the commands without the need of reinforcement.
    \item The system should be able to distinguish between commands and actions executed by the users.
\end{itemize}
\subsection{User characteristics}
\begin{itemize}
    \item Client: The expected skill set of the client is novice and that translates to the need for commands executed by them to be simple and intuitive. These gestures should be simple for in the case of recurrent visits clients should not need the use of aid to accomplish their interactions with the system.
    \item Waiter: The expected skill set of the waiter is expert and that translates to the use of more complex commands that could be executed by them allowing them to be gatekeep from the other user type. At the same time is not so complex that waiters need more than normal amount of time to execute them.
\end{itemize}
\subsection{Usability goals}
\begin{itemize}
    \item The gestures used by the client should be simple and easy to master.
    \item The gestures used by the waiter should have a certain level of complexity, this should avoid replication from the client side. But at the same time be understandable and trainable by the workforce.
\end{itemize}
\subsection{User experience goals}
\begin{itemize}
    \item Using the command interface should be an enjoyable to use.
    \item The system should be responsive in when receiving commands.
\end{itemize}
\section{Requirement fulfilment}
For the user interaction interface:
\begin{itemize}
    \item Hand gestures with leap motion sensors.
    \item Voice commands via phone app.
    \item Hand gestures with conventional video camera.
\end{itemize}
For the context aware interface there is just one implementation the use of led lights to represent the status of the current table. The only thing that changes is the position of them between table under glow, table border, ceiling light over the table.
For the user table recognition there is one implementation of pressure sensor on the sits.
\bibliography{mybib}
\end{document}
